---
title: "Listening to Customers is Not Enough to Uncover Thier Needs"
description: |
  Don't Confuse Salience with Importance.
authors:
  - name: Hari Sridhar, Vikas Mittal, Muzeeb Shaikh, and Ashwin Malshe
    url: https://ccubes.net
    affiliation: C-CUBES
    date: "`r Sys.Date()`"
output: distill::distill_article
categories:
- CEO
- Decision-making
- Customer value

#draft: false
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# Install
#install.packages("tm",repos = "http://cran.us.r-project.org")  
#install.packages("SnowballC",repos = "http://cran.us.r-project.org") 
#install.packages("wordcloud",repos = "http://cran.us.r-project.org") 
#install.packages("RColorBrewer",repos = "http://cran.us.r-project.org") 
#install.packages("wordcloud2",repos = "http://cran.us.r-project.org")
#install.packages("tibble",repos = "http://cran.us.r-project.org")
#install.packages("ggforce",repos = "http://cran.us.r-project.org")
#install.packages("ggplot2",repos = "http://cran.us.r-project.org")
#install.packages("hwordcloud",repos = "http://cran.us.r-project.org")

# Load
library("tm")
library("SnowballC")
library("wordcloud")
library("RColorBrewer")
library("wordcloud2")
library("tibble")
library("ggforce")
library("ggplot2")
library("hwordcloud")

```

## FOODCO's CEO Confuses Salience and Importance

The book **[FOCUS](https://focus-book.net/)** narrates the story of FOODCO, a lunch-focused restaurant chain with 22 locations in a major metropolitan city. 

During a strategy planning meeting, FOODCO's CEO says, *“We sell over a million meals a year because of our extensive menu of offerings and high quality. Last week, two customers from a restaurant thanked me for the expanded menu selection and high-quality food. We need to emphasize these benefits to improve customer value and sales.”* 

On the face of it, FOODCO's CEO seemed to be doing all the right things. He took the time to visit his restaurant, interact with the customers during service hours and talk to them about how they felt about FOODCO's offering. So if the customers told him they liked the menu selection and high-quality food, it seems reasonable to assume that FOODCO's strategy should be to focus on these areas right?

Not always right.

FOODCO's CEO bases his proposed strategy on **salience**—he easily recalls two benefits that customers have mentioned in conversations with him.The salience of a strategic area is measured by the probability with which a benefit is recalled and mentioned by a customer. In everyday life, salience is the extent to which some facts and perceptual elements are prominent and top-of-mind as well as easier to recall, remember, and imagine than others.

In this blog, we walk through the technicalities behind salience and importance, to avoid falling for the salience trap while formulating strategy.

## Capturing Salience from Customer Feedback

Executives frequently talk to stakeholders like customers, employees, suppliers, and peers. They then use portions of the conversations they recall in order to formulate strategy. 

As a former chef, FOODCO's owner loved to visit the restaurants when customer were dining and ask them about the quality of the food and the menu selection. After obtaining a transcript of the interviews, one could perform natural language processing to capture salience from customer feedback. The wordcloud below visually depicts the most frequently occurring themes in the conversations . 


```{r fragment1, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}

#text <- readLines(file.choose())

# Read the text file from internet
filePath <- "C:/Users/ssridhar/Dropbox/GitHub/Stratonomics/FOODCO.csv"
text <- readLines(filePath)

# Load the data as a corpus
docs <- Corpus(VectorSource(text))
inspect(docs)
toSpace <- content_transformer(function (x , pattern ) gsub(pattern, " ", x))
docs <- tm_map(docs, toSpace, "/")
docs <- tm_map(docs, toSpace, "@")
docs <- tm_map(docs, toSpace, "\\|")

# Convert the text to lower case
docs <- tm_map(docs, content_transformer(tolower))

# Remove numbers
docs <- tm_map(docs, removeNumbers)

# Remove english common stopwords
docs <- tm_map(docs, removeWords, stopwords("english"))

# Remove your own stop word
# specify your stopwords as a character vector
docs <- tm_map(docs, removeWords, c("food", "high","can","great")) 
# Remove punctuations
docs <- tm_map(docs, removePunctuation)
# Eliminate extra white spaces
docs <- tm_map(docs, stripWhitespace)

# Text stemming
# docs <- tm_map(docs, stemDocument)

dtm <- TermDocumentMatrix(docs)
m <- as.matrix(dtm)
v <- sort(rowSums(m),decreasing=TRUE)
d <- data.frame(word = names(v),freq=v)
head(d, 10)


#set.seed(1234)
#wordcloud(words = d$word, freq = d$freq, min.freq = 3,
        # max.words=30, random.order=TRUE, rot.per=0.35, 
        #colors=brewer.pal(8, "Dark2"))

```



```{r fragment2, echo=FALSE, message=FALSE, warning=FALSE}
#hwordcloud(text = d$word, size = d$freq, width = "100%", height = "200px",theme="darkblue")
wordcloud2(data=d, size=0.5, color='random-light', minRotation = -pi/6, 
           maxRotation = -pi/6, minSize = 10,shape="circle")

```

The visualization shows that the quality of the menu, tasty food, selection and of items were popular themes in the conversation. **You can scroll over the words to see how frequently they occurred in the conversations**. The visualization also shows that the minutes of wait time and need to reduce the menu came up as popular themes in the conversations. The FOODCO owner recalled the extensive menu and high quality food more than other items. Certain issues resonate with executives due to their own experiences. Since the FOODCO owner is a former chef. When customers talk about food variety and quality, it confirms the restaurant owner’s pre-existing notions (also called  confirmation bias). 

The figure below lists the most frequent words from the interviews. As we can see, the words **quality**, **menu**, and **tasty** are the three most salient aspects of the conversations, further illustrating why FOODCO's CEO argued that the strategy should be based on these items. 

More formally, we can obtain the frequency of the 

Most frequent Words are shown below




```{r fragment3, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
findFreqTerms(dtm, lowfreq = 4)
findAssocs(dtm, terms = "freedom", corlimit = 0.3)
head(d, 10)

lbls <- d[1:6,]$word
mostfreq <- d[1:6,]$freq
pctfreq <- round(mostfreq/sum(mostfreq)*100)
lbls <- paste(lbls, pctfreq) # add percents to labels
lbls <- paste(lbls,"%",sep="") # add % to labels

barplot(pctfreq, las = 2, names.arg = lbls,
        col ="lightblue", main ="Salience of strategic areas",
        ylab = "Percent Occurence of most frequent words",las=3)

#barplot(d[1:10,]$freq, las = 2, names.arg = d[1:10,]$word,
 #       col ="lightblue", main ="Most frequent words",
  #      ylab = "Word frequencies")

```




```{r fragment4, echo=FALSE, message=FALSE, warning=FALSE,results="hide"}
# Probability of Recall of EAch Strategic Area
slices <- c(55, 35, 5, 5)
lbls <- c("High quality food", "Expanded menu","Shorter Wait Time", "Parking")
pct <- round(slices/sum(slices)*100)
lbls <- paste(lbls, pct) # add percents to labels
lbls <- paste(lbls,"%",sep="") # ad % to labels
barplot(slices, las = 2, names.arg = lbls,
        col ="lightblue", main ="Salience of each strategic area",
        ylab = "Probability of Recall by FOODCO ownwer")

```


However, stakeholder input can be heavily biased for several reasons:

•	Individual customers mention issues that are not representative of the customer base. 
•	Certain issues resonate with executives due to their own experiences. For example, the FOODCO owner is a former chef. When customers talk about food variety and quality, it confirms the restaurant owner’s pre-existing notions (i.e., confirmation bias).
•	Executives seek out unstructured conversations with stakeholders who support their pre-existing views. Due to selection bias, they elicit only a narrow selection of views rather than a complete spectrum of views; this reinforces already salient information and ignores novel insights. The CEO of a company in the oilfield services business states: “Safety is critical to our company’s mission—we are very interested in listening to clients so we can learn more about their safety needs.” 

Though widely used in many industries, unstructured conversations do a poor job of eliciting salience because of confirmation and selection biases. Studies have shown that biases cannot be avoided even when using professional interviewers, such as branding experts or qualitative researchers. 




## Mathematical Intuition of Importance



## Steps in Calculating Importance

To calculate the importance of a strategy factor without mental biases, senior executives at a firm must implement the following steps:

1.	Identify the unit of interest. The unit may be customers, employees, geographic regions, product lines, territories, or business divisions.

2.	Develop a measurable metric for the relevant strategy outcome. The appropriate strategy outcome is usually customer value, as measured through surveys, or a financial metric, such as revenue, quantity sold, sales, margin, or ROI.

3.	Develop a performance metric for the strategy areas evaluated. The metric can be based on actual data (e.g., operational metrics), perceptions from customer or employee surveys, or secondary research (e.g., industry association ratings). Survey-based performance metrics provide useful insights only if the survey is carefully designed. 

4.	Use rigorous statistical analysis to isolate the magnitude of association between each strategy area and the relevant strategy outcome (show from regression, lasso). For most companies, the process involves engaging analytics experts. Going beyond simple correlations, the goal is to isolate the unique association between a strategy area and outcome after controlling for confounding factors. Relative importance can be calculated as the percent change in the desired outcome as a result of a unit shift in an input.

5.	Depict the relative importance of inputs. The percent change in the desired outcome as a result of a unit shift in an input can be used to prioritize strategy areas.

## Deriving Importance from Regression

To determine the importance of strategic areas, the restaurant chain conducts a customer study measuring satisfaction with each area as well as overall satisfaction. The strength of association between strategic area satisfaction and overall satisfaction represents the importance of each customer benefit(Figure 1).

A comparison of Panel A and B in Figure 1 shows that the strategic areas important for customers are not the areas salient to the restaurant-chain owner. Decades of research shows a weak to non-existent correlation between the salience and importance of customer benefits.  

 

## Strategy Dilemma at FOODCO

When the lunch-focused restaurant chain FOODCO was hit with stagnating sales, its CEO and owner wanted to improve his strategy. He focused on the many different menu items he believed would preserve FOODCO’s “high quality”—freshly prepared sandwiches, soups, and salads. Yet, customer surveys showed that customers wanted a fast dining experience with a short wait time, a simple menu with few items, ample parking, and a bill lower than $12 per meal, drinks included. The survey results contrasted starkly with the strategy direction FOODCO’s owner charted.
When FOODCO’s owner read the survey findings, he said, “This validates what has been clear to me all along. We have to lead and not be led. Too often, customers don’t know what they want, and we have to shape their needs. Look at Apple. We need a winning strategy that differentiates our brands, and we can do that by offering the largest selection of freshly prepared foods at the lowest price point in the marketplace.”






## Salience vs. Importance


Many salient benefits may not actually be important to customers, and vice versa.  Due to its ease and higher probability of recall, salient information is often incorrectly perceived as being important. Many times, people incorrectly emphasize salient information in their decision-making. The way a job candidate dresses may be salient to an interviewer but it may be completely unimportant for job performance. 

To arrive at a focused and customer-based strategy, executives need to base their strategy on **importance**. The importance of a strategic area is the strength of the association between the strategic area and a desired outcome, such as overall satisfaction, word-of-mouth, or purchase behavior. Many benefits are important to customers, even though they may not be salient.Customers who have read about a local plane crash may consider safety to be a salient issue. But when traveling on a long-haul flight, they may actually find benefits like comfort (seating, legroom, blankets, and pillows) and pricing (tickets, free luggage, and carry-ons allowed) to be the most important drivers of their overall satisfaction with the trip.

## Conclusion: Listening is Not Enough

A firm’s value proposition and customer value equation should be based on benefits important to its customers and strategic areas in which the customers perceive the firm’s performance as being better than its competitors. Many firms focus only on salient customer benefits through "listening sessions" which risk ignoring truly important benefits. This is a mistake. 

To counteract the damaging effects of salience and prioritize strategy areas based on importance, executives must first conduct a rigorous analysis. They must clearly define their desired outcome and a set of critical inputs. The inputs’ importance must be calculated based on how strongly each is linked to the desired outcome. The process involves linking performance in different strategy areas to the outcome while statistically controlling for confounding extraneous factors. 

This brief describes the correct approach to measuring the importance of customer benefits and evaluating a firm’s performance as perceived by customers. 







